\title To Identify the characteristics of SSL applications

\brief Encrypted traffic is indistinguishable from noise. At least, the raw data is. When sent over a radio connection at a constant rate the only information one can get is the raw data. However on a network like the internet, the protocols used to transmit encrypted data give away a great deal of information. This paper seeks to answer the question: can we identify information about an encrypted connection by looking at this additional information. Can we identify the software the user is using? How fast can we make a positive identification?

The Internet provides two protocols for commonly used communications:
\list
  \item UDP
  \item TCP

UDP communications involve individual packets with a destination. They are not stateless.

TCP is stateful, it maintains a connection. Most SSL applications operate over TCP, this is for a number of reasons:

\list
  \item Exchanging an encryption key to begin a communication is costly, therefore it is best to keep a connection open for a long period
  \item SSL encryption is sensitive to order, TCP maintains order

For this reason, TCP leaks a lot of information about an SSL stream. This information is:

\list
  \item Individual packet size
  \item Individual packet flags
  \item Period between last packet

Additionally, the way a program is can influence many of these values above. If packets are written to buffers properly, if there is serious computation between certain operations etc. This can
be present in the shape of the traffic, allowing us to fingerprint certain applications.

Ways of identifying applications:
  Bytes in recognizeable chunks (multiples of 512?)
  Large burst of traffic at traffic initiation
  Length of sessions (all a certain time like say 10 mins?)
  Source port
  Keepalives?
  Nagle algorithm
  Window size


  \section

  Because projects such as ToR and Freenet lack the critical mass / exposure to normal use, it is easy to justify blocking them alltogether in the name of national security, that they are only used by paedophiles and criminals etc. For this reason it is beneficial to make them indistinguishable from normal ssl applications so they cannot be blocked automatically.
